%!TeX root =  ../../Marvus-in-Cpp.tex

This application originally began as a purely CLI-based project (which is also the reason for its name, \textit{ConsoleArt}). As the project evolved, a \gls{gui} was later added. Development started at a time when C++17 was the newest standard, so the use of modern features such as smart pointers was adopted gradually throughout the project.

\section{Technologies Used}

\subsection{wxWidgets}
This project is written mainly in C++ and utilize \gls{wxwidgets} for the \gls{gui}.  \gls{wxwidgets} is cross-platform and utilize naive GUI libraries for each supported platform.

\subsection{SQLite}

\subsection{ConsoleLib}
\texttt{ConsoleLib} is my custom library developed to simplify the creation of CLI applications. 
It provides an abstract \texttt{IConsole} interface and several platform-specific implementations:

\begin{itemize}
    \item \textbf{DefaultConsole} – A basic implementation using standard output (\texttt{std::cout}) without any additional formatting features.
    \item \textbf{UnixConsole} – Adds support for text coloring and formatting through ANSI escape codes commonly available on Unix-like systems.
    \item \textbf{WindowsConsole} – Inherits from \texttt{UnixConsole} and enables UTF-8 output on Windows while ensuring compatibility with ANSI escape codes.
\end{itemize}

The library also includes additional utility modules such as an argument parser and other helpers commonly required in CLI tools, making it reusable across multiple projects.

\section{Commiting a git commit}
\begin{table} [H]
	\centering
	\catcode`\-=12
	\begin{tabular}[c]{|| c | c ||}
	\hline
		\multicolumn{2}{||c||}{ \textbf{Commit type cheat table}} \\
	\hline
 		 \textbf{Type} & \textbf{Repository change} \\
	\hline
		\textcolor{purple}{Feat:} & A new feature is added \\
	\hline
		\textcolor{blue}{Fixed:} & A bug is fixed \\
	\hline
		\textcolor{orange}{Docs:} & A documentation is updated \\
	\hline
		\textcolor{black}{Refactor:} & A code change that is not affecting functionality \\
	\hline
		\textcolor{brown}{Test:} & A code change in unit tests \\
	\hline
		\textcolor{gray}{Chore:} & A repository maintenance action \\
	\hline
		\textcolor{magenta}{Version x.y} & When new version is released for clearer commit history \\
	\hline
	\end{tabular}
	\caption{Types of commit headers}
	\label{table:cmtHeaders}
\end{table}