%!TeX root =  ../../Marvus-in-Cpp.tex

\section{Technologies Used}

\subsection{GTK 4}
This project is written mainly in C++ and utilize \gls{gtk} for the \gls{gui}.  \gls{gtk} is cross-platform and it has a modern linux-like look, but that is alright as I work on this project on linux.

\input{chapters/introduction/subsubsection_why_gtk_4.tex}

\subsection{SQLite}
This project use SQLite for simplicity as main focus is on C++ and GUI. So this application will not produce accurate statistics as SQLite do not support accurate decimal data type and use only double. I will compare results from this application with results from my Java application that uses BigDecimal for accurate decimal calculations.

\subsection{ConsoleLib}
\texttt{ConsoleLib} is my custom library developed to simplify the creation of CLI applications. 
It provides an abstract \texttt{IConsole} interface and several platform-specific implementations:

\begin{itemize}
    \item \textbf{DefaultConsole} – A basic implementation using standard output (\texttt{std::cout}) without any additional formatting features.
    \item \textbf{UnixConsole} – Adds support for text coloring and formatting through ANSI escape codes commonly available on Unix-like systems.
    \item \textbf{WindowsConsole} – Inherits from \texttt{UnixConsole} and enables UTF-8 output on Windows while ensuring compatibility with ANSI escape codes.
\end{itemize}

The library also includes additional utility modules such as an argument parser and other helpers commonly required in CLI tools, making it reusable across multiple projects.

\subsection{MiniZ}
MiniZ is simple C library for working with zip files which are used to import data from my Java application to this one. 

\subsection{Boost}
The Boost C++ Libraries are open source, peer-reviewed, portable and free. Created by experts to be reliable, skillfully-designed, and well-tested.